\documentclass[compress]{beamer}
\setbeamercolor{normal text}{fg=black}
\beamertemplatesolidbackgroundcolor{white}
\setbeamercovered{transparent, still covered={\opaqueness<1->{0}}, again covered={\opaqueness<1->{30}}}
\usecolortheme[named=black]{structure}
\definecolor{links}{HTML}{98AFC7}
\hypersetup{colorlinks,linkcolor=,urlcolor=links}
\usepackage{caption}
\captionsetup{labelformat=empty}
\setbeamertemplate{navigation symbols}{} 

\definecolor{dark-red}{rgb}{0.75,0.10,0.10} 
\definecolor{grey}{rgb}{.3, 0.3, .3}
\definecolor{amber}{rgb}{1.0, 0.75, 0.0}
\definecolor{arylideyellow}{rgb}{0.91, 0.84, 0.42}
\definecolor{azure(colorwheel)}{rgb}{0.0, 0.5, 1.0}
\definecolor{blue}{rgb}{0, .1, 0.42}

\usepackage[scaled]{helvet}
\renewcommand*\familydefault{\sfdefault} %% Only if the base font of the document is to be sans serif
\usepackage[T1]{fontenc}
\usepackage{setspace}
%\usepackage{beamerthemesplit}
\usepackage{graphics}
\usepackage{Sweave}

\usepackage[normalem]{ulem}

\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{amssymb}
\usepackage{wrapfig}
\def\labelitemi{\textemdash}
\setbeamertemplate{frametitle}{
  %\begin{centering}
    \vskip10pt
    \insertframetitle
    \par
  %\end{centering}
} 
\title[Better Know Your IP]{Better Know Your IP}
\author[]{\vspace{.15cm}\\}
\date[]{}
\begin{document}

\newenvironment{large_enum}{
\Large
\begin{itemize}
  \setlength{\itemsep}{7pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
}{\end{itemize}}

\begin{comment}

setwd(paste0(githubdir, "know_your_ip/know_your_ip/presentation/"))
tools::texi2dvi("kip.tex", pdf = TRUE, clean = TRUE) 
setwd(basedir)

\end{comment}
 \frame
  {
    \titlepage
  }

\begin{frame}
\frametitle{Example Application: Cybersecurity Analysis}
\begin{large_enum}
\item[-]<2-5> General Workflow: ETL \pause \pause $\leadsto$ `Analytics' \pause $\leadsto$ `Outliers' \pause $\leadsto$ `Deep Dive'
\item[-]<6-7> Push Button Time Allocation within Data Scientists:
        \begin{itemize}
        \item[-]<7->Analytics ($\sim$ 25\%)
        \item[-]<7->Deep Dive (\color{red}{$\sim$ 75\%})
        \end{itemize}
\item[]<8-12> A {\color{red}\sout{Deep Dive}} Dip Into Deep Dive 
  \begin{itemize}
   \item[-]<9->  Manual sifting of small data 
   \item[-]<10-> Find `interesting' outliers 
   \item[-]<11-> Tell story about those outliers
   \item[-]<12-> Including, why the outlier was flagged as such 
  \end{itemize} 
\item[]<13-> Aim: Better ways of learning about, and from outliers.
\end{large_enum}
\end{frame}

\begin{frame}
\frametitle{Better ways of learning about, and from outliers}
 \begin{large_enum}
  \item[-]<2-5> Three components:
    \begin{itemize} 
      \item[-]<3-> Data driven account of why an outlier is an outlier
      \item[-]<4-> Data driven inference about patterns of outliers 
      \item[-]<5-> \color{red}{Diving Deeply More Quickly}
    \end{itemize}
  \item[-]<6-> (Better) Know Your IP
    \begin{itemize}
      \item[-]<7-> Gets `known knowns' and `easily knowns'
      \item[-]<8-> Where: Lat/Long, City, Country, Time zone
      \item[-]<9-> Which ports are open, which services are running
      \item[-]<10-> Ping and traceroute
      \item[-]<11-> Blacklisted or not, and for what
      \item[-]<12-> Zmap and Zgrab scans of IPv4
    \end{itemize}
\end{large_enum}
\end{frame}

\begin{frame}
\frametitle{Notes and Concerns}
\begin{large_enum}
  \item[-]<1-5> Geocoding:
    \begin{itemize} 
      \item[-]<2-> Start with DB of known `landmarks'
      \item[-]<3-> Compute maximum distance to last router from multiple landmarks using max. Internet speed
      \item[-]<4-> Gives an approximate bounding box. Take centroid of that.
      \item[-]<5-> Average geolocation error can be hefty. For instance, \href{http://www.geoipinfo.com/}{GeoIPInfo} puts me $\sim$ 30 miles away
    \end{itemize}
  \item[-]<6-9> Time Zone
    \begin{itemize}
      \item[-]<7-> Globe split into 24 Time Zones. Conditional on lat/long, we know time zone.
      \item[-]<8-> But countries create own rules 
      \item[-]<9-> India, for instance, has 30 minute offset. Or for e.g., Mountain Time
    \end{itemize}
  \item[-]<10-11> Active scanning (ping, traceroute)
  \begin{itemize}
    \item[-]<11-> You give away your location. \color{red}{{\tt tcpdump}}.
  \end{itemize}
\end{large_enum}
\end{frame}

\begin{frame}[fragile]
\frametitle{Know, Know Your IP}
\begin{large_enum}
\item[-]<2>Links to:
  \begin{itemize}
  \item[-]<2-> GeoNames
  \item[-]<2-> MaxMind
  \item[-]<2-> Virustotal 
  \item[-]<2-> IpVoid
  \item[-]<2-> AbuseIPDB
  \item[-]<2-> Shodan
  \item[-]<2-> Censys
  \item[-]<2-> Ping
  \item[-]<2-> Traceroute
  \item[-]<2-> tzwhere
  \end{itemize}
\item[-]<3> Rate limits for free tier
\item[-]<4> \color{red}{Use it for a handful of IPs}
\end{large_enum}
\end{frame}

\begin{frame}[fragile]
\frametitle{Know, Know Your IP}
\begin{large_enum}
\item[-]<2-> Installation\\\normalsize
\begin{verbatim}
pip install know_your_ip

# If traceroute not installed on Linux
sudo apt-get install traceroute 
\end{verbatim}
\item[-]<3-> Components:

\begin{itemize}
\item[1. ]<4-> Configuration file: \\
\begin{verbatim}
know_your_ip.cfg

[abuseipdb]
enable = 1
user_id = 1234
key = a0fbe08ccef49245179490713e551b589
cat_catid = abuseipdb_cat_catid.csv

[ipvoid]
enable = 1

...
\end{verbatim}
\end{itemize}
\end{large_enum}
\end{frame}

\begin{frame}[fragile]
\frametitle{Components of KIP}
\begin{large_enum}
\item[]<1->
\begin{itemize}
\item[2. ]<1-> What columns do you want
\begin{verbatim}
columns.txt

# Ping
ping.timeout
ping.count
ping.max
 ...

# abuseipdb API
abuseipdb.bad_isp
abuseipdb.categories
abuseipdb.reports
abuseipdb.total
 ...
\end{verbatim}
\end{itemize}
\end{large_enum}
\end{frame}

\begin{frame}[fragile]
\frametitle{Using KIP}
\begin{verbatim}
python know_your_ip.py  

# Paths
--file path_to_input_file (default input.csv)
--config path_config_file   (default know_your_ip.cfg)
--output path_to_output_file (default output.csv)

# Max connections (multi-threaded)
--maxconn MAX_CONN

# From/to Row
--from from_row
--to to_row

# Verbose
--verbose verbose

\end{verbatim}
\end{frame}

\begin{frame}[fragile]
\frametitle{Actually Using KIP}
\begin{verbatim}

# For one/few IP(s)
python know_your_ip.py 94.31.29.154 
python know_your_ip.py 94.31.29.154 204.2.197.211

# File, some rows
python know_your_ip.py --file input_small.csv --from 1
 --to 2

\end{verbatim}
\end{frame}
\end{document}
